\papertitle

### 2012-10-12 manuscript.tex
Added intro citations, updated platform and experiment sections.

We also introduce a new ornithopter MAV, the 13 gram H$^2$Bird. It 
features clap and fling wings, improves upon a previous design by 
utilizing a carbon fiber airframe, tail rotor, and elevator, and carries a 
payload of 2.8 grams. We augment the ornithopter's built-in 
gyroscope-based control with a ground station, which has power and weight 
requirements appropriate for deployment on 30 gram a ground vehicle. The ground 
station provides heading estimates to the ornithoper by running a 
real-time motion tracking algorithm on a live video stream. This allows 
the ornithopter to reliably negotiate flight through narrow openings.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%TODO(ryan)
The power, size, and weight constraints of micro air vehicle (MAV) 
platforms significantly limit on-board sensing and computational 
resources, and thus the complexity of the control and state estimation 
algorithms which can be executed on-board. These constraints are 
particularly severe for flapping wing MAVs, a class of MAVs that have inherently superior 
safety, efficiency, and noise profile to rotor craft MAVs, but at the 
expense of payload weight.
%Intro portion about previous works in ornithopter coorperative control/
%modeling ( won't necessarily stay in this spot)

Autonomous control of flapping winged MAVs is a complex undertaking, because
of the non-linear flight dynamics and underactuation of the system due to size
constraints. Many of the methods for controlling these platforms make
extensive use of GPS in outdoor environments [CITATIONS] and extensive motion
capture systems in indoor environments. While operating indoors, using GPS to 
estimate the pose of the MAV is not possible, and motion capture requires expensive
and stationary modification of the environment. The power and payload limits on MAVs
make on-board sensing difficult, so multi-agent cooperative control schemes are 
apt solutions.

@@

% TODO Fill in test # per battery
Variations in the H$^2$Bird hand launch cause the system to respond differently 
for otherwise identical initial initial conditions. In addition, the H$^2$Bird 
battery was changed approximately every [10] tests, adding more variation to
the H$^2$Bird performance by affecting the motor power output. The effects of 
these noisy factors is considered in Section ~\ref{sec:performance}.

\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/experiment_cartoon.pdf}
\caption{Conceptual sketch of experimental environment.}
\label{fig:experiment_cartoon}
\end{figure}
%TODO label experiment cartoon

>>>>

We also introduce a new ornithopter MAV, the 13 gram H$^2$Bird. It 
features clap and fling wings, improves upon a previous design by 
utilizing a carbon fiber airframe, tail rotor, and elevator, and carries a 
payload of 2.8 grams. We augment the ornithopter's built-in 
gyroscope-based control with a ground station, which has power and weight 
requirements appropriate for deployment on a 30 gram ground vehicle. The ground 
station provides heading estimates to the ornithoper by running a 
real-time motion tracking algorithm on a live video stream. This allows 
the ornithopter to reliably negotiate flight through narrow openings.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%TODO(ryan)
The power, size, and weight constraints of micro air vehicle (MAV) 
platforms significantly limit on-board sensing and computational 
resources, and thus the complexity of the control and state estimation 
algorithms which can be executed on-board. These constraints are 
particularly severe for flapping wing MAVs, a class of MAVs that have inherently superior 
safety, efficiency, and noise profile to rotor craft MAVs, but at the 
expense of payload weight.
%Intro portion about previous works in ornithopter cooperative control/
%modeling ( won't necessarily stay in this spot)
Modeling and control of flapping wing MAVs is a well studied subject. 
Shigeoka discusses velocity and altitude control in \cite{Shigeoka:ornithopter}. In 
\cite{delfly:design} deCroon et al.

Due to restrictive payload weights, much previous work on guidance of flapping wing 
with cameras depends on powerful offboard processing. Baek demonstrated altitude control 
with an external camera\cite{baek:altitude}. de Croon et al. demonstrated obstacle 
avoidance with an onboard camera\cite{delfly:avoid}. [However, these papers have not studied
the system blah blah blah.]

Autonomous control of flapping winged MAVs is a complex undertaking because
of the non-linear flight dynamics and underactuation of the system due to size
constraints. Many of the methods for controlling these platforms make
extensive use of GPS in outdoor environments [CITATIONS] and extensive motion
capture systems in indoor environments. While operating indoors, using GPS to 
estimate the pose of the MAV is not possible, and motion capture requires expensive
and stationary modification of the environment. The power and payload limits on MAVs
make on-board sensing difficult, so multi-agent cooperative control schemes are 
apt solutions.

@@

% TODO Fill in test # per battery
In total, [50+] good trials were run over a variety of starting positions. 
Variations in the H$^2$Bird hand launch caused the system to respond very 
differently for similar initial conditions. In addition, the H$^2$Bird 
battery was changed approximately every [10] tests, adding more variation to
the H$^2$Bird performance by affecting the motor power output. The effects of 
these noisy factors is considered in Section ~\ref{sec:performance}.

\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/experiment_cartoon.pdf}
\caption{Conceptual sketch of experimental environment. Dimensions are in meters.}
\label{fig:experiment_cartoon}
\end{figure}
%TODO label experiment cartoon
